NEED TITLE

### 2014-11-13 ms.tex
Added captions to rho, vr, etc graphs for 132

\begin{figure*}
\plottwo{Track_0132_000_rho.png}{pdf_frame_0132_0000.png}
\plottwo{Track_0132_000_vr.png}{Track_0132_000_mass.png}
\caption{Tracking plot for density and associated pdf graphs for two regions.  The density graphs have slopes of -3/2, -2, and -5/2 shown for reference.  The upper density frame on the left shows a consistent slope matching the -3/2 reference line very nicely.  The pdf graphs show three volumes, one at 1pc, one at 2pc, and one at 5pc.  \label{fig:Track_and_pdf_000}}
\end{figure*}

\begin{figure*}
\plottwo{Track_0132_002_rho.png}{pdf_frame_0132_0002.png}
\plottwo{Track_0132_002_vr.png} {Track_0132_002_mass.png}
\caption{Tracking plot for density and associated pdf graphs for two regions.  The density graphs have slopes of -3/2, -2, and -5/2 shown for reference.  The upper density frame on the left shows a consistent slope matching the -3/2 reference line very nicely.  The pdf graphs show three volumes, one at 1pc, one at 2pc, and one at 5pc.  \label{fig:Track_and_pdf_002}}
\end{figure*}

>>>>

\begin{figure*}
\plottwo{Track_0132_000_rho.png}{pdf_frame_0132_0000.png}
\plottwo{Track_0132_000_vr.png}{Track_0132_000_mass.png}
\caption{Tracking 132 000  These plots show various data for one of the particles formed in the simulation.  The upper left graph shows the density profile, with reference lines indicating slopes of -3/2, -2, and -5/2.  The slope between $0.02$pc and $0.4$pc approximately matches the -5/2 reference line.  The plot on the upper right shows the pdf function related to volumes of 1pc, 2pc, and 5pc.  The bottom left shows a plot of the radial velocity and turbulent velocity associated with the particle.  The lower right graph shows the radial density profile of the particle.    \label{fig:132 000 graphs}}
\end{figure*}

\begin{figure*}
\plottwo{Track_0132_002_rho.png}{pdf_frame_0132_0002.png}
\plottwo{Track_0132_002_vr.png} {Track_0132_002_mass.png}
\caption{Tracking 132 002  These plots show the data for a different particle formed in the simulation at the same time as the previous plots.  The upper left graph of the density in the region neatly matches the -3/2 slope.  The pdf graph in the upper right again shows the plots for volumes related to $1$pc, $2$pc, and $5$pc.  The lower left plot demonstrates the loose connection between the radial velocity and the turbulent velocity.  The graph on the lower right again shows the density profile of this second particle.     \label{fig:132_002_graphs}}
\end{figure*}
